\chapter{Conclusion and Future Scope}
\section{Conclusion}
\paragraph{}After successfully testing the various segments of our project so far we can conclude that this product can be a very ideal device for surveillance in bounded areas. the robot responds to all the keys in ideal time frame and moves accordingly in different directions. The accuracy of these movements make it a very idealistic equipment.

The live feed capturing from the camera resent on the robot is also very accurate and has minimal or no delay at all. The clarity of the same is astonishing.\\
\newline
After testing and analysing the project so far these are the advantages that we can conclude upon:
\begin{enumerate}
\item Low cost
\item Wireless system makes it compact
\item Easily portable
\item System operates at near real time
\item Makes remote controlling very easy
\item Huge add-ons like obstacle avoidance is possible
\item Eliminates human error
\item Nature friendly as it uses solar charging
\item Ensures data privacy of the user
\end{enumerate}

\section{Future Scope}
\paragraph{}The project that we have implemented has immense future prospective and an abysmal scope for future enhancements. There are limitless possibilities of its usage in the industry. However our main aim was to implement a low cost compact handy remote controlled robot due to which the choices we had for implementation were limited and narrowed down only to a few.\\
\newline
Future applications of the product are as follows:
\begin{enumerate}
\item \textbf{Security management systems}: The robot can be used for patrolling in campuses of various organizations spread over an area. The camera and microphone present on it can provide access to live feed of any corner of the campus at any given point of time. A server setup in the security room can store data in a safe and secure manner.

\item \textbf{Wildlife photography and videography}: The robot can be used by a wildlife photography team in order to observe the flora and fauna for endless hours . As the robot can manage obstacles, it is easier for it to move around in rough terrains . This helps the organization to study the wildlife without disturbing it with human presence. Example mine caves.

\item \textbf{Survey of underground tunnels}: the product can be applicable for uses in data logging and observational surveys that need to be conducted in inaccessible places. For example a survey of underground metro lines or sewage tunnels.

\item \textbf{Information gathering}: The device can be excellent for active reconnaissance. Military observation of a region to locate an enemy or ascertain strategic features. the safe and secure data storage assures national security.
\end{enumerate}