\addcontentsline{toc}{chapter}{References}
\begin{thebibliography}{99}
\bibitem{IEEE Paper}
J. Bae, D. Lee and K. Cho, "Speed and Direction Control of Two In-wheel BLDC Motors for the Self-Driving Surveillance Robot," 2020 6th International Conference on Mechatronics and Robotics Engineering (ICMRE), 2020, pp. 17-21, doi: 10.1109/ICMRE49073.2020.9065011.

\bibitem{IEEE Paper}
M. Hamza, M. Atique-ur-Rehman, H. Shafqat and S. B. Khalid, "CGI SCRIPT AND MJPG VIDEO STREAMER BASED SURVEILLANCE ROBOT USING RASPBERRY PI," 2019 16th International Bhurban Conference on Applied Sciences and Technology (IBCAST), 2019, pp. 947-951, doi: 10.1109/IBCAST.2019.8667217.

\bibitem{IEEE Paper} 
A. U. Bokade and V. R. Ratnaparkhe, "Video surveillance robot control using smartphone and Raspberry Pi," 2016 International Conference on Communication and Signal Processing (ICCSP), 2016, pp. 2094-2097, doi: 10.1109/ICCSP.2016.7754547.

\bibitem{IEEE Paper} 
H. R. and M. H. Safwat Hussain, "Surveillance Robot Using Raspberry Pi and IoT," 2018 International Conference on Design Innovations for 3Cs Compute Communicate Control (ICDI3C), 2018, pp. 46-51, doi: 10.1109/ICDI3C.2018.00018.

\bibitem{IEEE Paper} 
M. F. Alvi, F. Junejo, M. W. Baloch and A. J. Rajput, "RoboCop; A Robust Surveillance Robot," 2018 1st International Conference on Advanced Research in Engineering Sciences (ARES), 2018, pp. 1-8, doi: 10.1109/ARESX.2018.8723270.

\bibitem{IEEE Paper} 
S. Meghana, T. V. Nikhil, R. Murali, S. Sanjana, R. Vidhya and K. J. Mohammed, "Design and implementation of surveillance robot for outdoor security," 2017 2nd IEEE International Conference on Recent Trends in Electronics, Information \& Communication Technology (RTEICT), 2017, pp. 1679-1682, doi: 10.1109/RTEICT.2017.8256885.

\bibitem{IEEE Paper} 
N. K. Raghavendra and K. Padmavathi, "Solar Charge Controller for Lithium-Ion Battery," 2018 IEEE International Conference on Power Electronics, Drives and Energy Systems (PEDES), 2018, pp. 1-5, doi: 10.1109/PEDES.2018.8707743.

\bibitem{Website}
Raspberry Pi L298N Interface Tutorial | Control a DC Motor\\
\textit{https://www.electronicshub.org/raspberry-pi-l298n-interface-tutorial-control-dc-motor-l298n-raspberry-pi/}

\bibitem{Website}
Flask For Python3\\
\textit{https://youtu.be/Z1RJmh\_OqeA}

\bibitem{Website}
Solar Battery Charger (LiPo/Li-Ion)\\
\textit{https://youtu.be/kEttqWJrdww}

\bibitem{Website}
Web Basics - Accessing JSON data from URL\\
\textit{https://youtu.be/kIRp6HOQzP8}

\bibitem{Website}
Run a python script forever on Raspberry Pi\\
\textit{https://gist.github.com/skynet-05/f5445b8ad046a08b9469884c12a1a443}

\bibitem{Books}
Raj Kamal, ‖Internet of Things-Architecture and design principles‖, McGraw Hill
Education.

\bibitem{Books}
Holger Karl \& Andreas Willig, "Protocols And Architectures for Wireless Sensor
Networks" , John Wiley, 2005.

\bibitem{Books}
Feng Zhao \& Leonidas J. Guibas, ―Wireless Sensor Networks- An Information
Processing Approach", Elsevier, 2007.
%\bibitem{•} \emph{•} \url{•}
\end{thebibliography}
